\section{Compared Methods}

\subsection{Genetic Algorithm}

\textbf{Genetic Algorithm.} EvoDrive Lab includes a custom genetic algorithm that evolves policy weights generation by generation. In the frozen paper protocol, the GA runs for 12 iterations per seed and serves as the most natural fit for the live multi-car simulation because population turnover is directly visible in the interface and replay outputs. The GA therefore acts as both a competitive benchmark method and a useful qualitative reference for the visual side of the project.

\subsection{NEAT}

\textbf{NEAT.} The benchmark also integrates \texttt{neat-python} as a topology-evolving baseline based on NeuroEvolution of Augmenting Topologies \cite{stanley2002}. It uses the same environment and evaluation suites as the other methods and also runs for 12 iterations per seed in the paper configuration. This allows comparison between direct parameter evolution and evolving network structure under a shared benchmark budget.

\subsection{Lightweight PPO-style Baseline}

\textbf{PPO-style baseline.} The repository contains a lightweight in-repo implementation of PPO-style policy optimization inspired by PPO \cite{schulman2017}. In the paper configuration it runs for 8 outer iterations and 8192 total timesteps per seed. This baseline is intentionally modest: it is included to provide a policy-gradient comparison point, not to stand in for a large production RL stack such as a heavily tuned Stable-Baselines3-style pipeline.

\subsection{Shared Comparison Protocol}

All three methods share the same observation interface, action interface, train/validation/test suites, and evaluation metrics. The benchmark therefore isolates differences in training behavior rather than changing environment semantics between algorithms. This common protocol is important for interpretation: when one method underperforms, the explanation should be sought primarily in optimization behavior rather than in a mismatch of observation spaces, action spaces, or evaluation rules.
